ECE498:~Senior Capstone Project I\\\textbf{\underline{Project Proposal}}\\ \vspace{0.5in} Project Title: Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle \vspace{1.0in} \author{Hannah Grady and Nicholas Nauman\\ Advisor: Dr.~Suruz Miah}

### 2021-12-06 proposal.tex
Feedback on the proposal

\begin{figure}[htb]
    \centering 
\begin{subfigure}{0.25\textwidth}
  \includegraphics[width=2in]{figs/inkscape/steeringModelArchitecture}
\end{subfigure}\hfill
\begin{subfigure}{0.25\textwidth}
  \includegraphics[width=2in]{figs/inkscape/brakeModelArchitecture}
\end{subfigure}\hfill
\begin{subfigure}{0.25\textwidth}
  \includegraphics[width=2in]{figs/inkscape/accelerationModelArchitecture}
\end{subfigure}

\vspace{36pt}
\begin{subfigure}{0.25\textwidth}
  \includegraphics[width=2in]{figs/inkscape/shiftModelArchitecture}
\end{subfigure}\hfill
\begin{subfigure}{0.25\textwidth}
  \includegraphics[width=2in]{figs/inkscape/speedControlModelArchitecture}
\end{subfigure}\hfill
\begin{subfigure}{0.25\textwidth}
  \includegraphics[width=2in]{figs/inkscape/speedModelArchitecture}
\end{subfigure}
\vspace{16pt}
\caption{Autonomous Vehicle Subsystem Functional Block Diagrams}
\label{fig:subFunctionalBlock}
\end{figure}

>>>>

\begin{figure}[htb]
    \centering 
\begin{subfigure}[b]{0.48\linewidth}
  \centering 
  \includegraphics[width=2.5in]{figs/inkscape/steeringmodelarchitecture}
  \caption{}
  \label{fig:steeringmodelarchitecture}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
  \centering
  \includegraphics[width=2.5in]{figs/inkscape/brakeModelArchitecture}
  \caption{}
  \label{fig:brakeModelArchitecture}
\end{subfigure}
\\
\begin{subfigure}[b]{0.48\textwidth}
  \centering 
  \includegraphics[width=2.5in]{figs/inkscape/accelerationModelArchitecture}
  \caption{}
  \label{fig:accelerationModelArchitecture}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
  \centering 
  \includegraphics[width=2.5in]{figs/inkscape/shiftModelArchitecture}
  \caption{}
  \label{fig:shiftModelArchitecture}
\end{subfigure}
\\
\begin{subfigure}[b]{0.48\linewidth}
  \centering
  \includegraphics[width=2.5in]{figs/inkscape/speedControlModelArchitecture}
  \caption{}
  \label{fig:speedControlModelArchitecture}
\end{subfigure}
\begin{subfigure}[b]{0.48\linewidth}
  \centering
  \includegraphics[width=2.5in]{figs/inkscape/speedModelArchitecture}
  \caption{}
  \label{fig:speedModelArchitecture}
\end{subfigure}
\caption{Block diagrams of autonomous vehicle subsystems:~\subref{fig:steeringmodelarchitecture} steering subsystem,~\subref{fig:brakeModelArchitecture} brake subsystem,~\subref{fig:accelerationModelArchitecture} acceleration subsystem,~\subref{fig:shiftModelArchitecture} shift subsystem,~\subref{fig:speedControlModelArchitecture} speed control subsystem, and~\subref{fig:speedModelArchitecture} speed subsystem.}
\label{fig:subFunctionalBlock}
\end{figure}
